---
title: ""
output:
    html_document:
      runtime: shiny
      css: www/style_slim.css
      includes:
        before_body: www/header.html
---

```{r setup, include=FALSE}
knitr::opts_chunk$set( message = F, warning = F, out.width = "100%",echo = FALSE)

zg_colors <- c("#222831","#393e46","#d65A31","#EEEEEE","#FFCF99","#FFCF99")

corp_colors <- c("#88BdBc","#254e58","#112d32","#4f4a41","#6E6658")

clean_mod <- c("#17252A","#2B7A78","#3AAFa9","#DEF2f1","#FEFFFF")

nature <- c("#687864","#31708E","#5085A5","#8FC1E3","#F7F9FB")

peaceful_mod <- c("#844D36","#474853","#86B3D1","#AAA0A0","#8E8268")

corp_serious <- c("#265077","#022140","#494B68","#1E4258","#2D5F5D")
library(tidyquant)
library(tidyverse)
library(DT)
library(highcharter)



```


<style>

.btn-default.active.focus, .btn-default.active:focus, .btn-default.active:hover, .btn-default:active.focus, .btn-default:active:focus, .btn-default:active:hover, .open>.dropdown-toggle.btn-default.focus, .open>.dropdown-toggle.btn-default:focus, .open>.dropdown-toggle.btn-default:hover {
    outline: none;
    color: #333;
    background-color: #Ba996E;
    border-color: #Ba996E;
}


.main {
position : relative;
}


.mb-wrap {
margin : 20px auto;
padding : 20px;
position : relative;
text-align: center;
width: 75%;

}

.mb-wrap p {
margin : 0;
padding : 0;
}

.mb-wrap blockquote {
margin : 0;
padding : 0;
position : relative;
}

.mb-wrap cite {
font-style : normal;
}



blockquote {
    border-left: none;
}


.mb-style-2 blockquote p {
color : #Ba996E;
display : inline;
font-family : Baskerville, Georgia, serif;
font-style : italic;
font-size : 28px;
line-height : 46px;
}

.mb-attribution {
text-align : center;
}

.mb-author {
color : #Ba996E;
font-size : 18px;
font-weight : bold;
padding-top : 10px;
text-shadow : 0 1px 1px rgba(255, 255, 255, 0.1);
text-transform : uppercase;
}

button {
    outline: none;
}


cite a {
color : #Ba996E;
font-style : italic;
}

cite a:hover {
color : #Ba996E;
}
</style>

  
  
```{r}

values <- reactiveValues(default = 0)



quote <- eventReactive(input$go, {
    
  read_csv('C:\\Users\\zg5280\\Desktop\\QuantViz_2.0\\QuantViz\\Trash\\biz_quotes.csv') %>% sample_n(1)
  
  }, ignoreNULL = T)


start <- reactive({

if(values$default == 0){

read_csv('C:\\Users\\zg5280\\Desktop\\QuantViz_2.0\\QuantViz\\Trash\\biz_quotes.csv') %>% sample_n(1)

    
}
  
})


observeEvent(input$go,{
           values$default <- input$go
      })



renderUI(

  
  
    
  
  HTML(
    paste(
      '
<section class="main">
<div class="mb-wrap mb-style-2">
<blockquote >
<p>',


ifelse(values$default == 0,start()$text,quote()$text)



,'
</p>
</blockquote>
</div>

<div class="mb-attribution">
<p class="mb-author">',
ifelse(values$default == 0,start()$author,quote()$author)
,'</p>
</div>

</section>

      
      
      
      
      
      '
    )
  )
  
)

```

```{r}
actionButton("go","new quote")

```

